---
title: "This is a template for a reproducible report"
format: html
bibliography: references.bib
---

## Technical Setting

### Libraries

```{r libraries}
library(tidyverse)

```

### Functions

```{r functions}
compute_interaction <- function(a,b) a*b

```


## Download Data

The data is embedded in this report via base64 encoding. 
You can download it `r xfun::embed_file("data/sim_data.csv", "sim_data.csv", "here")` 
or from this [github repository](https://github.com/SonjaHahn/RepReport_Quarto).

The source code of this report can be retrieved 
`r xfun::embed_file("MyReport.qmd", "MyReport.qmd", "here")`.


## Data Import

*Note: This is a simulated data set used for teaching purposes based on @spangenberg2005jobr.*

```{r data import}
data <- read.csv("Data/sim_data.csv")

```

## Data Preprocessing 

```{r data preprocessing}
data$interaction <- compute_interaction(data$iV_Music, data$iV_Scent)

```

## Descriptives

```{r Descriptive Statistics}
table(data$iV_Music, data$iV_Scent) 

```

## Research Questions

**Optional.**


### Graphical Overview

```{r Graphs}
boxplot(dV_Evaluation ~ iV_Music * iV_Scent, data = data)

```


### Analysis 1

```{r First Analysis}
model <- lm(dV_Evaluation ~ iV_Music * iV_Scent, data = data)

summary(model)

```

*Probably you will need more chunks for analysis.*

## Session Info

```{r}
sI <- sessionInfo(package = NULL)
print(sI)

# osVersion

```
